sentiment-analysis

### 2016-08-04 eda/sentiment-analysis.Rmd
randomized sample of reviews

I'll read in the first 500,000 observations of the Yelp reviewers data, which has been written to a csv file.
```{r}
reviews <- read_csv("../clean_data/reviews.csv")
```

@@

```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
  labs(x = "# of reviews",
       y = "Average Stars",
       color = "AFINN") +
  theme_bw()
```

>>>>

I'll read 500,000 randomly sampled observations of the Yelp reviewers data, which has been written to a csv file.
```{r}
reviews <- read_csv("../clean_data/yelp_reviews.csv")
reviews <- reviews %>% 
  sample_n(500000)
```

@@

Below, I'll plot word frequency vs 
```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
  labs(x = "# of reviews",
       y = "Average Stars",
       color = "AFINN") +
  theme_bw()
```
